Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-09 submission/NatCom_appendix.tex
appendix updated

We provide a github repository for this paper that includes Jupyter notebooks that fully reproduce all results (as well as many other results)~\cite{kdd20_sub_repo}.
All results have been produced using the \texttt{WeightWatcher} tool (v0.2.7)~\cite{weightwatcher_package}.
The ImageNet and OpenAI GPT pretrained models are provided in the current 
pyTorch~\cite{pytorch} and Huggingface~\cite{huggingface} distributions, as specified in the \texttt{requirements.txt}~file.

@@

In the \texttt{ww-colab} folder of our github repo, we provide several Google Colab notebooks which can be used to reproduce the results of Section~\ref{sxn:all_cv_models}.
The ImageNet-1K and other pretrained models are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The data for each regression can be generated in parallel by running each Google Colab notebook (i.e., \texttt{ww\_colab\_0\_100.ipynb}) simultaneously on the same account.
The data generated are analyzed with \texttt{ww\_colab\_results.ipynb}, which runs all regressions and which tabulates the results presented in Table~\ref{table:results}.

>>>>

We provide a github repository for this paper that includes Jupyter notebooks that fully reproduce all results (as well as many other results)~\cite{kdd20_sub_repo}.
All results have been produced using the \texttt{WeightWatcher} tool (v0.2.7)~\cite{weightwatcher_package}.
The ImageNet and OpenAI GPT pretrained models are provided in the current 
pyTorch~\cite{pytorch} and Huggingface~\cite{huggingface} distributions.

@@

In our github repository, we provide several python Juoyter Google Colab anotebooks,
as well as previously generated data,  which can be used to reproduce the results of Section~\ref{sxn:all_cv_models}, 
and using the \texttt{WeightWatcher} tool (version 0.2.7), as described in Table~\ref{table:notebooks}.
The ImageNet-1K and other pretrained models are taken from the pyTorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository~\cite{osmr}.
The full  \texttt{WeightWatcher} results are provided in the datasets: \texttt{[data/osmr/data...xlsx]},
last generated in January 2020, using the Google Colab notebooks: \texttt{[ww\_colab/ww\_colab...ipynb]}.
These data files are analyzed with the \texttt{OSMR-Analysis.ipynb} python Juyter Notebook,
which runs all regressions and which tabulates the results presented in Table~\ref{table:results}
and generates the figures in Figures~\ref{fig:summary_regressions_A}-\ref{fig:summary_regressions_I}.
